---
output: 
  pdf_document:
  html_document:
    includes:
      in_header: "header.html"
title: "Confidence Interval for Means"
params:
  xbar:
    value: 23 
  sigma:
    value: 4
  n:
    value: 53 
  confidence:
    value: 0.95
---
```{r params, include=FALSE}
#params
xbar<-params$xbar 
sigma<-params$sigma 
n<-params$n
confidence<-params$confidence
#computed values
zstar <- -1*qnorm((1.0-confidence)/2.0) 
sqrtOfN <- sqrt(n)
E <- zstar * (sigma)/sqrtOfN
xbarMinusE <- xbar - E
xbarPlusE <- xbar + E
```

Find a `r confidence*100`% confidence interval when the sample mean is $\bar x=`r xbar`$, the standard deviation is $\sigma=`r sigma`$ and the sample size is $n = `r n`$.

First we find the E involved, using the confidence level to compute the appropriate critical z-value:

\begin{align}
E & = (z^\star)\frac{\sigma}{\sqrt{n}} \newline
  & = (`r round(zstar,3)`)(\frac{`r sigma`}{\sqrt{`r n`}}) \newline 
  & = (`r round(zstar,3)`)(\frac{`r sigma`}{`r round(sqrtOfN,3)`}) \newline
  & = (`r round(zstar,3)`)(`r round(sigma/sqrtOfN,3)`) \newline
  & = `r round(E,3)`
\end{align}

Then we find the two endpoints:

\begin{align}
\text{left endpoint} & = \bar x - E = `r xbar`-`r round(E,3)` = `r round(xbar-E,3)` \newline 
\text{right endpoint} & = \bar x + E = `r xbar`+`r round(E,3)` = `r round(xbar+E,3)` 
\end{align}

So the confidence interval is $(`r round(xbarMinusE,1)`,`r round(xbarPlusE,1)`)$

```{r include=FALSE}
#\begin{align}
#E = (z^\star)\frac{\sigma}{\sqrt{n}} 
#  = (`r round(zstar,3)`)(\frac{`r sigma`}{\sqrt{`r n`}})
#  = (`r round(zstar,3)`)(\frac{`r sigma`}{`r round(sqrtOfN,3)`}) 
#  = (`r round(zstar,3)`)(`r round(sigma/sqrtOfN,3)`)
#  = `r round(E,3)`
#\end{align}
```
