---
title: "Image Latex Demo"
output:
  html_document:
    mathjax: null
    pandoc_args: [
      "--webtex=http://chart.googleapis.com/chart?cht=tx&chl="
    ]
params:
  a:
    input: slider
    label: This is a
    max: 50
    min: 1
    step: 3
    value: 12
  b:
    input: slider
    label: This is b
    max: 50
    min: 1
    step: 3
    value: 45
---

```{r params, echo=FALSE}
    a<-params$a; 
    b<-params$b; 
```

This example shows creating data URL versions of images for graphics and formulas. Use the webtex argument to pandoc to point to the service that will make the graphics.  

This is good for copying and pasting into some email clients (gmail,etc)  

Display LaTeX rendered at data URL images:  

$$
z =\frac{a}{b}
  =\frac{`r a`}{`r b`}
$$

Why is the above rendered on the left side, instead of the middle?

Inline LaTeX as data URL image: $z = b - a =`r b`-`r a` = `r b-a`$ Text after on same line  

Finally below is a dataURL embedded image:  

```{r area, echo=FALSE}
plot(cars)
```

