---
title: "Normal Area Between"
params:
  a: 4.2 
  b: 5.5 
  mu: 5 
  sigma: 2 
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r options, eval=FALSE, include=FALSE}
options(repr.plot.width=4, repr.plot.height=4)
```

```{r params, include=FALSE}
if(!exists("params")) {
    params<-list(a=1.23,b=1.75,mu=0,sigma=1.0)
}
a<-params$a 
b<-params$b 
mu<-params$mu 
sigma<-params$sigma 
```

```{r computed, include=FALSE}
lowerz<-(a-mu)/sigma
upperz<-(b-mu)/sigma
areaB <- round(pnorm(upperz),4)
areaA <- round(pnorm(lowerz),4)
areaBetween <- round(areaB-areaA,4)
```

We are going to find the area between the two x-values $x=a=`r a`$ and $x=b=`r b`$ by first converting them both to z-values, then finding the area between those z-values.

First lets find the "lower z-value". This is the z-value for the left endpoint ($x=a=`r a`$):

$$
z =\frac{x-\mu}{\sigma} =\frac{`r a`-`r mu`}{`r sigma`} =\frac{`r a-mu`}{`r sigma`} =`r round(lowerz,2)`
$$

Next lets find the "upper z-value". This is the z-value for the right endpoint ($x=b=`r b`$):

$$
z =\frac{x-\mu}{\sigma} =\frac{`r b`-`r mu`}{`r sigma`} =\frac{`r b-mu`}{`r sigma`} =`r round(upperz,2)`
$$

Now we can find the area between these two z-values by subtracting the left tail area for each one.       

Using the standard normal table we find the left tail area for $z=`r upperz`$ is $`r areaB`$ and the left tail area for $z=`r lowerz`$ is $`r areaA`$.     

We subtract these two areas to find the area between them: 

$$
\text{area between}=`r areaB` - `r areaA`=`r areaBetween`
$$
