---
title: "Standard Normal-Area Between Z Values"
params:
  a: -1.0
  b: 2.1
jupyter:
  kernelspec:
    display_name: R
    language: R
    name: ir
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(include=FALSE)
knitr::opts_chunk$set(fig.align='center', fig.width=4, fig.height=3)
library(ggplot2)
```

```{r params}
# This is here for jupyter versions
if(!exists("params")) {
    params<-list(a=-1.0,b=2.1)
}
a<-params$a
b<-params$b
```

```{r calculated}
areaB <- round(pnorm(b),4)
areaA <- round(pnorm(a),4)
areaBetween <- round(areaB-areaA, 4)
```

We are going to find the area between the two z-values by using the standard normal (z) table.

Here $a =`r a`$ and $b =`r b`$

Here is a picture of the area that we want:

```{r area, echo=FALSE, include=TRUE}
#change dev to svg if need to

dat <- data.frame(x=c(-3.5, 3.5))
labelA <- sprintf("a = %s",a)
labelB <- sprintf("b = %s",b)
ggplot(dat, aes(x=x)) +
	stat_function(fun=dnorm) +   
	stat_function(fun=dnorm,     
		      xlim = c(a,b), 
		      geom="area", 
		      fill="green", 
		      alpha=0.3) +
	labs(x = "Z", y = "") +       
	geom_hline(yintercept=0) +
	scale_x_continuous(breaks = seq(-3, 3, by = 1.0)) +
	scale_y_continuous(breaks = seq(0, .4, by = 0.2)) +
	annotate("text", 
		 x = a, 
		 y = -0.02, 
		 label = labelA) +
	annotate("text", 
		 x = b, 
		 y = -0.02, 
		 label = labelB)
```

First we find the left tail area for z-value on the right: $b =`r b`$

$$
\text{left tail area for b} = `r areaB`
$$

Then we find the left tail area for the z-value on the left $a =`r a`$:

$$
\text{left tail area for a} = `r areaA`
$$

Finally we find the area between the two z-values by subtracting the left tail area up to b by the left tail area up to a. This leaves us with the area between the two z-values:

$$
\text{area between}=`r areaB` - `r areaA`=`r areaBetween`
$$
