---
Title: "Test Problem"
output:
  html_document: 
    default
params:
  x:
    input: slider
    label: This is x 
    max: 50
    min: 1
    step: 3
    value: 40
  mu:
    input: slider
    label: This is mu 
    max: 80
    min: 50
    step: 1
    value: 60
  sigma:
    input: numeric
    label: This is sigma 
    max: 20 
    min: 0 
    step: 1 
    value: 5 
  gender:
    choices:
    - male
    - female
    inline: yes
    input: radio
    label: 'Gender:'
    value: male
  region:
    choices:
    - east
    - west
    - north
    - south
    input: select
    label: 'Region:'
    value: north
  word:
    input: text
    label: 'Word of the day:'
    placeholder: Type the word of the day
    value: 'nothing'
---

```{r params, echo=FALSE}
    x<-params$x; 
    mu<-params$mu; 
    sigma<-params$sigma; 
```
## Test Header 1  

The below shows we can run R code. Here we look at the cars dataset:   

```{r summary}
str(cars)
summary(cars)
```
Test that we can access the params from the header:  

```{r printparams}
x
mu
sigma
```
Next show that we can embed plots.

```{r plot, echo=FALSE}
plot(cars)
```
  
Test that we can do inline r expressions:   

The value of x is: `r x` This still on same line.   
The value of mu is: `r mu` This still on same line.   

Test that we can do static inline LaTeX with dollar sign: $\frac{2}{3}$. This text is after.     

And try to do static display math LaTeX with double dollar signs:  

$$
z=\frac{x-\mu}{\sigma}
$$

Next dynamic inline LaTeX with dollar sign: $z=\frac{`r x`-`r mu`}{`r sigma`}$. This is after.  

Next dynamic display LaTeX using the params:

$$
z = \frac{x-\mu}{\sigma}
  = \frac{`r x`- `r mu`}{`r sigma`}
$$

Here is some dynamicly evaluated display LaTeX:  

$$
z = \frac{x-\mu}{\sigma}
  = \frac{`r x` - `r mu`}{`r sigma`}
  = \frac{`r x-mu`}{`r sigma`}
  = `r (x-mu)/sigma`
$$
